---
title       : Developing Data Products App
subtitle    : Self-Assessment Tool for Test Performance
author      : Kurt Schuepfer
job         : Data Scientist Trainee
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose of the App

- Students are often told they have to study hard in order to get good results. 
- The purpose of this app is to allow students to see firsthand the effects of their study time on their test performance.

---


## How the App Works

- Load the app 
- Enter your test scores for five separate tests
- Enter how many minutes you spent studying for each test
- Click 'Submit' button
- See your results in the tables and plot on the right side of the screen


---

## An Example:

- Say your raw test score data is as follows:
```{r, echo = FALSE}
scoresVector <- c(87.30, 100, 73.10, 85, 80)
minutesVector <- c(90, 150, 60, 120, 90)
testData <- data.frame(Scores = scoresVector,Minutes = minutesVector)
testData
```


- You would enter those numbers in the app.
- The summary statistics output would look like this:
```{r, echo=FALSE}
                        testMean <- (mean(scoresVector))
                        testMedian <- median(scoresVector)
                        testMin <- min(scoresVector)
                        testMax <- max(scoresVector)
                        testSD <- sd(scoresVector)
                        
                        data.frame("Test_Average" = testMean, testMedian, testMin, testMax, testSD)

testData <- data.frame(Scores = scoresVector,Minutes = minutesVector)
```



---

## An Example

- And the scatterplot would look like this:  
```{r, echo=FALSE}
plot <- plot(testData$Minutes, testData$Scores, 
                     main = "Academic Performance vs Preparation Time",
                     ylim = c(0, 100),
                     ylab = "Test Score (% out of 100)", 
                     xlim = c(0, max(minutesVector)),
                     xlab = "Study Time (minutes)",
                     abline(lm(Scores ~ Minutes, data = testData)))
plot
```
---
